Validation of Visual Statistical Inference, Applied to Linear Models

### 2012-06-29 paper_jasa.tex
model extimates table caption

The model in Equation \ref{eqn:mixed} provides the subject and lineup specific probability of successful evaluation as 
\begin{equation} \label{eqn:mixed_power}
\hat p_{\ell i} =  g^{-1}(W_{\ell i} \hat {\delta} +  Z_{\ell i}  \hat {\tau}_{\ell i}).
\end{equation}

@@

\begin{table}[hbtp]
\caption{Parameter estimates of model in Equation \ref{eqn:mixed}.}
\begin{center}
\begin{tabular}{cccc}
  \hline
 &  \multicolumn{2}{c} {Fixed effect}  & Random effect\\
 \cline{2-3}
 Experiment & Estimate & Std. error & Variance\\
  \hline
  1 & 0.39 & 0.0093 & 0.0077 \\ 
  2 & 1.22 &  0.0196 &  0.0455 \\ 
  3 &  & & \\ 
   \hline
\end{tabular}
\end{center}
\label{tbl:model_par}
\end{table}

>>>>

Using the inverse {\it logit} link function, $g^{-1}(.)$, from  Equation \ref{eqn:mixed} we obtain the the estimate of subject and lineup specific probability of successful evaluation as 
\begin{equation} \label{eqn:mixed_power}
\hat p_{\ell i} =  g^{-1}(W_{\ell i} \hat {\delta} +  Z_{\ell i}  \hat {\tau}_{\ell i}).
\end{equation}

@@

\begin{table}[hbtp]
\caption{Parameter estimates of model in Equation \ref{eqn:mixed}. Estimates are highly significant with $p$-value $<$  0.0001 for all three experiment data.}
\begin{center}
\begin{tabular}{cccc}
  \hline
 &  \multicolumn{2}{c} {Fixed effect}  & Random effect\\
 \cline{2-3}
 Experiment & Estimate & Std. error & Variance\\
  \hline
  1 & 0.39 & 0.0093 & 0.0077 \\ 
  2 & 1.22 &  0.0196 &  0.0455 \\ 
  3 &  & & \\ 
   \hline
\end{tabular}
\end{center}
\label{tbl:model_par}
\end{table}
